\documentclass{article}

% If you're new to LaTeX, here's some short tutorials:
% https://www.overleaf.com/learn/latex/Learn_LaTeX_in_30_minutes
% https://en.wikibooks.org/wiki/LaTeX/Basics

% Formatting
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[titletoc,title]{appendix}

% Math
% https://www.overleaf.com/learn/latex/Mathematical_expressions
% https://en.wikibooks.org/wiki/LaTeX/Mathematics
\usepackage{amsmath,amsfonts,amssymb,mathtools}
\usepackage{dirtree}
% Algorithms
% https://www.overleaf.com/learn/latex/algorithms
% https://en.wikibooks.org/wiki/LaTeX/Algorithms
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{algorithmic}
% References
% https://www.overleaf.com/learn/latex/Bibliography_management_in_LaTeX
% https://en.wikibooks.org/wiki/LaTeX/Bibliography_Management
\usepackage{biblatex}
\addbibresource{references.bib}

% Title content
\title{COS 460a Quiz 2}
\author{Dastanbek Samatov}
\date{April 21, 2020}

\begin{document}

\maketitle

% Abstract
\begin{abstract}
    Implement a library for arithmetic operations with Polynomials in C++.
\end{abstract}

% Introduction and Overview
\section{Introduction and Overview}

The library consists of a class Polynomial with its respective arithmetic methods and
other overloaded built-in operators, such as comparison operators, assignment, 
increment and decrementation operators. Polynomials are stored in a \textbf{map}, where
key is the power and value is the coefficient of respective member of the Polynomial.
For example, a polynomial p 
\begin{equation}
    p = x^4 + 3x^3 - 2x^2 + 3 
\end{equation}
is assigned to the following map: \textbf{[ [0, 3], [1, -2], [2, 3], [3, 1] ]}

Overview of the file structure:
\dirtree{%
.1 /.
.2 doc.
.3 doc.pdf.
.2 main.cpp.
.2 PolyOperations.cpp.
.2 PolyOperations.h.
.2 test.txt.
.2 tests.cpp.
}
% Example Subsection
\subsection{Constructors}
\textbf{Polynomial} class has four types of constructors: \textbf{default, constructor from 
vector, constructor from map and constructor from another instance of the class.}

% Example Subsubsection
\subsection{Arithmetical Operations}
An instance of \textbf{Polynomial} class has add, subtract, multiply, divide methods along
with several utility functions. Along with these methods, native arithmetic 
operators (+, -, *, /) are also overloaded for the Polynomial class.

%  Theoretical Background
\section{Theoretical Background}

Algorithm for adding and subtracting Polynomials is rather trivial. Multiplication is 
slightly more complicated but it also doesn't deserve specific mention. Some other
problems I had was zero coefficients after arithmetical operations. So I implemented
a methods which finds those coefficients and erases them from the map of the object. 

Another objective was to deal with the Null Polynomial which resulted from the arithmetic
operations, since in the clean() method I was iterating through the elements of map,
it was essential to handle the iterator so that the next node is not empty. Otherwise,
the program would give Segmentation Fault.
% Algorithm Implementation and Development
\newpage
\section{Algorithm Implementation and Development}
Following is the Pseudocode on which I based the implentation of division of polynomials.
Worst time complexity is O($n^2$) and the best is O(1). It receives dividen and divisor
as an argument and return a vector of maps with quotient and remainder.


\begin{algorithm}[H]
    \SetAlgoLined
    \KwResult{returns (q, r) }
    \If{degreeD smaller than 0 }{
        error
    }

     q = 0\;
     \While{degreeN greater or equal to degreeD}{
      d = D (shifted by degreeN-degreeD)\;
      q(degreeN-degreeD) = N(degreeN)/d(degreeD)\;
      d = d * q(degreeN - degreeD)\;
      N = N - d\;
     }
     r = N\;
     return (q,r)\;
     \caption{Polynomial Long Division Pseudocode}
    \end{algorithm}
% Summary and Conclusions
\section{Conclusions}
The code is well-documneted, with necessary comments and structure. When
writing the algorithms I used mainly Wikipedia and GeekForGeeks website
for research. Most of the methods of C++, such as assignment, comparison, incrementation
operators are overloaded for the convenience of computing polynomials.

\section{References}
\begin{thebibliography}{2}
    \bibitem{RoseettaCode}
    $Polynomial long division (n.d.). Retrieved from https://rosettacode.org/wiki/Polynomial_long_division$
    \bibitem{Wikipedia}
    $Polynomial. (2020, April 13). Retrieved from https://en.wikipedia.org/wiki/Polynomial
    $
    \bibitem{Long Division}
    $Polynomial long division. (2020, January 14). Retrieved from https://en.wikipedia.org/wiki/Polynomial_long_division$
\end{thebibliography}

% Appendices
\begin{appendices}
\end{appendices}

\end{document}
